Plug-and-play dual-tree algorithm runtime analysis

### 2015-08-14 bounds-files/general-runtime-bound.tex
Pull definition of \theta out of Lemma 4.
Clarify what the monochromatic case actually is.

\begin{equation}
\theta = \max\left\{\min\left[O(N \log_2(\delta_q / \delta_r)),
O(N^2)\right], \; 0\right\}.
\end{equation}
\end{lemma}

@@

When we consider the monochromatic case (where $S_q = S_r$), the results
trivially simplify.

>>>>

\begin{equation}
\max\left\{\min\left[O(N \log_2(\delta_q / \delta_r)),
O(N^2)\right], \; 0\right\}.
\end{equation}
\end{lemma}

For convenience, we define a term that encapsulates this bound.

\begin{defn}
Define $\theta$ as a bound on the number of extra reference recursions tha
happen after the last query recursion.  Then,

\begin{equation}
\theta = \max\left\{\min\left[O(N \log_2(\delta_q / \delta_r)), O(N^2)\right],
\; 0\right\}.
\end{equation}
\end{defn}

@@

When we consider the monochromatic case (where $S_q = S_r$)\footnote{In the
monochromatic case, we do not take a point as its own nearest neighbor, so
slight modification of {\tt BaseCase()} is necessary.  The runtime bound result
remains unchanged.}, the results trivially simplify.
